Stack Safety as a Security Property

### 2020-06-30 main.tex
nit
Started lazy integrity in new style

\subsection{Program Structre}

@@

    \definition{Observable Integrity}

      Observable integrity weakens eager integrity by allowing a returned state
      to differ from its call state at high integrity components, provided the
      observable behavior of the induced trace from the return matches that of
      an idealized state whose high integrity components do match the call
      state.

      Given a contour, a call state, and a returned state, we define a
      ``rollback'' function \(\mathit{roll} : \CONTOURS \times \MACHS \times
      \MACHS \rightarrow \MACHS\). The rollback returns a state that matches
      the call state on those components that are high integrity in its
      contour, and matches the return state on low integrity components:
      \[\mathit{roll}(\contour,\mach_c,\mach_r)(\component) =
      \begin{cases}
        \mach_c(\component) & \contour(\component) = (\HIGHINT,\_) \\
        \mach_r(\component) & \contour(\component) = (\LOWINT,\_) \\
      \end{cases}\]

      Intuitively, the result of a rollback is an idealized state that
      reflects changes to accessible components, but ignores the callee's
      interference with the caller's data. Then the observable behavior of the
      resulting trace is the standard to which we expect the real trace to
      conform.

      A system enjoys observable integrity with regard to \(\callmap\) and 
      \(\codemap\) if for any initial state \(\mach_0\) and each adjacent pair
      of a call state \(\mach_c\) and a state \(\mach_e\) with policy state
      \(\pol_e\) in the trace induced by
      \(\mpstate{\mach_0}{\mathit{pinit}(\mach_0)}\) where
      \(\callmap(\mach_c) = n\) and \(\codemap(\mach_e) = \funid\),
      if \(\mpstate{\mach_e}{\pol_e} \hookrightarrow \MPT | \ret{\mach_c}\)
      with the return state \(\mach_r\) at the end of \(\MPT\), then the
      following holds.

      Let \(\contour = \mathit{Cof}(\mach_c,\funid,n)\) describe the security
      levels of the call and
      \(\mach_r' = \mathit{roll}(\contour,\mach_e,\mach_r)\). The induced
      traces \(\mpstate{\mach_r}{\pol_r} \hookrightarrow \MPT\) and
      \(\mach_r' \hookrightarrow \machT'\) must be equivalent up to
      possible policy failure: \(\MPT \sim_P \machT'\).

>>>>

\subsection{Program Structure}

@@

    \definition{Observable Trace Integrity}

      Suppose a function \(f\) calls another function \(g\) with contour
      \(\contour\). If \(g\) alters an address below its stack frame, where
      \(\contour\) is \(\HIGHSEC\), the trace from the entry point to the
      return will not enjoy Trace Integrity. But if \(f\) immediately
      overwrites the overwritten location, the illegal write can be safely
      ignored, as it will never affect the behavior of the program.
      {\em Observable trace integrity} captures this intuition by guaranteeing
      that the final state, instead of being identical to the initial one,
      has the same behavior as it would if the writes had not occurred.

      Let \(\contour\) be a contour and \(\MPT\) be a finite \(\MPOTRACE\)
      whose initial machine state is \(\mach_e\). \(\MPT\) satisfies {\em trace
      integrity} with respect to \(\contour\) if the trace induced by its final
      state, \(\mpostate{\mach_r}{\pol}{\obs}\), is an observational prefix of
      that induced by an idealized state \(\mach_r'\) that agrees with
      \(\mach_r\) on all components marked \(\HIGHSEC\) in \(\contour\).
      Formally we define a rollback function, \(\mathit{roll}\), that takes
      two machine states and produces a third.
      %
      \[\mathit{roll}(\contour,\mach_e,\mach_r)(\component) =
      \begin{cases}
        \mach_c(\component) & \contour(\component) = (\HIGHINT,\_) \\
        \mach_r(\component) & \contour(\component) = (\LOWINT,\_) \\
      \end{cases}\]

      If \(\mach_e\) is an entry to a call with contour \(\contour\) and
      \(\mach_r\) its return, \(\mathit{roll}(\contour,\mach_e,\mach_r)\)
      agrees with \(\mach_e\) on every component the callee should not change,
      but with \(\mach_r\) on those components that it is permitted to change.
      So the observable behavior that follows is the idealized behavior to
      which we compare the trace from \(\mach_r\), which must prefix it (to
      account for premature halts due to policy violations.)
      %
      \[\begin{split}
        \text{\sc ObsInt}_\contour ~ \MPT \triangleq
          & \MPT = \mpostate{\mach_e}{\pol_e}{\obs_e} \dots
            \mpostate{\mach_r}{\pol_r}{\obs_r} \Rightarrow \\
        & \mpstate{\mach_r}{\pol_r} \hookrightarrow \MPT' \Rightarrow \\
        & \mathit{roll}(\contour,\mach_e,\mach_r) \hookrightarrow \machT' \Rightarrow \\
        & \pi_o(\MPT') \lesssim_O \pi_o(\machT')
      \end{split}\]

    \definition{Observable Stack Integrity}

      A system enjoys {\em observable integrity} with regard to \(\callmap\)
      and  \(\codemap\) if for any initial state \(\mach_0\) and each
      transition with entry state \(\mpostate{\mach_e}{\pol_e}{\obs_e}\) and
      contour \(\contour\) in the induced trace from
      \(\mpstate{\mach_0}{\mathit{pinit}(\mach_0)}\), if
      \(\mpstate{\mach_e}{\pol_e} \hookrightarrow \MPT | \ret{\mach_e}\),
      then \(\text{\sc ObsInt}_\contour ~ \MPT\).
